### 2017-01-31 local-capability-machine.tex

  Then $\exists W' \futurestr W$, $\hs_r$, $\hs' \ldotp$
  $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs']{n-i}{W'}$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item By induction on $n$. In other words, assume that the theorem already
    holds for all $n' < n$.
  \item The case that $i = 0$ is impossible, since
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
    \ms_f)\neq (\halted,\Phi)$ for any $\Phi$. Assume w.l.o.g. that $i = 1+i'$
  \item 
  \end{enumproof}
\end{proof}

>>>>

  Then $\exists W' \futurestr W$, $\hs_r$, $\hs' \ldotp$
  $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and $\heapSat[\hs']{n-i}{W'}$
\end{lemma}
\begin{proof}
  \begin{enumproof}
  \item By induction on $n$. In other words, assume that the theorem already
    holds for all $n' < n$.
  \item $i \neq 0$, since
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
    \ms_f)\neq (\halted,\Phi)$ for any $\Phi$. \\
    Therefore, assume w.l.o.g. that $i = 1+i'$,
    \begin{equation*}
      (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f) \step \var{conf'} \step[i'] (\halted,\Phi)
    \end{equation*}
  \item $\start \leq \addr \leq \addrend$, $\perm \in \{ \exec,\rwx, \rwlx \}$
    and $\var{conf'} =
    \sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
    \uplus \ms_f))$\\
    By definition of
    $(\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus \ms_f)
    \step \var{conf'}$, using the fact that $\var{conf'} \neq \failed$ (since it
    is not possible that $\failed \step[i'] (\halted,\Phi)$)
  \item We do a case analysis on
    $\memheap(a)$
    \begin{enumproof}
    \item Case $\memheap(a) = \jmp{\lv}$:
    \item Case $\memheap(a) = \jnz{\lv}{\rv}$:
    \item Case $\memheap(a) = \move{\lv}{\rv}$:
    \item Case $\memheap(a) = \load{\lv}{\hv}$:
    \item Case $\memheap(a) = \store{\hv}{\rv}$:
    \item Case $\memheap(a) = \plus{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \lea{\lv}{\rv}$:
    \item Case $\memheap(a) = \restricttwo{\lv}{\rv}$:
    \item Case $\memheap(a) = \subseg{\lv}{\rv}{\rv}$:
    \item Case $\memheap(a) = \isptr{\lv}{\rv}$:
    \item Case $\memheap(a) = \getp{\lv}{\lv}$:
    \item Case $\memheap(a) = \getl{\lv}{\lv}$:
    \item Case $\memheap(a) = \getb{\lv}{\lv}$:
    \item Case $\memheap(a) = \gete{\lv}{\lv}$:
    \item Case $\memheap(a) = \geta{\lv}{\lv}$:
    \item Case $\memheap(a) = \fail$: Contradiction, since then
      $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
      \uplus \ms_f)) = \failed$, so we have that $\failed \step[i']
      (\halted,\Phi)$ which is not possible.
    \item Case $\memheap(a) = \halt$:
      \begin{enumproof}
      \item
        $\sem{\decode(\memheap(\addr))}((\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
        \uplus \ms_f)) = (\halted, (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs
        \uplus \ms_f))$\\
        By definition of $\sem{\cdot}$
      \item Then $i' = 0$ and $\Phi =
        (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
        \ms_f)$. Follows from $(\halted,
        (\reg\update{\pcreg}{((\perm,\gl),\start,\addrend,\addr)},\hs \uplus
        \ms_f)) \step[i'] (\halted,\Phi)$
      \item For $W' = W$, $\ms_r = \emptyset$ and $\ms' = \ms$, we have that
        $\memheap[\Phi] = \hs' \uplus \hs_r \uplus \ms_f$ and
        $\heapSat[\hs']{n-1}{W'}$ (using Lemma~\ref{heap-sat-dc}).
      \end{enumproof}
    \end{enumproof}
  \end{enumproof}
\end{proof}
